Verifying Demonstrations

### 2017-09-30 protocol.tex
Changes disposition of protocol section

>>>>

We will now describe the protocol in more details.
We will describe it in the same order as outlined above:
starting with the storage and its required properties, then constructing the 
participation proof (shares) and submitting the proof shares to storage.
Finally, we will conclude with how to verify the proofs and produce the 
participation count.

\subsection{Constructing the participation-proof shares}
